SAT Competition 2020\tnoteref{title}

### 2020-12-17 paper/main.tex
refined ipasir benchmark section; finished sequential codebase overview

With the introduction of IPASIR (Re-entrant Incremental Solver API), the incremental library track took place for the first time in SAT~Race~2015~\cite{Balyo:2015:SATRace}, and then again in SAT~Competitions 2016 and 2017. 
In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.

\paragraph{Backbone Detection}

The application $\mathsf{genipabones}$ reads a formula from a given file and transforms it using the dual rail encoding, i.e., it replaces each $x$ by $p_x$ and each $\overline{x}$ by $n_x$ and adds clauses of the form ($\overline{p_x} \vee \overline{n_x}$). 
Incrementally, each variable is then checked if it is a backbone variable or not. 
For this application, we selected $50$ of the smallest and easiest satisfiable problems of previous SAT competitions.

\paragraph{Essential Variables Calculation}

%Given a satisfiable formula $F$, a variable $x$ is essential for the satisfiability of $F$ if a truth value must be assigned to $x$ in each satisfying partial assignment of F. 
The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula by testing each variable using the dual-rail encoded formula. 
For this application, we used the same easy satisfiable problems as in the Backbone Detection application.

\paragraph{Longest Simple Path Computation}

@@

\paragraph{MaxSAT}

The application $\mathsf{genipamax}$ is a trivial partial MaxSAT solver based on adding activation literals to soft clauses and 
subsequent incremental optimization using a cardinality constraint~\cite{Philipp:2015:PBLib} and assumptions. 
For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.

\paragraph{QBF}
$\mathsf{Ijtihad}$ is a solver for Quantified Boolean Formulas (QBFs). 
The solver tackles the a formula iteratively, using counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}.
For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.

\paragraph{Planning}
$\mathsf{Pasar}$ is a planer which is based on the principles of counter-example guided abstraction refinement(CEGAR)~\cite{Froleyks:2019:Pasar}. 
For this application, we selected $50$ sas planning instances.

@@

The SAT solvers of Armin Biere arguably belong to the best and most well-known independent code-bases. 
Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
CaDiCal came up in SAT Competition 2017 and has been award winning since then. 
The reimplementation of CaDiCal in the new SAT solver Kissat set a new standard in sequential SAT solving in this competition (see Section~\ref{}).

>>>>

Ihe incremental library track was first introduced in SAT~Race~2015 and then took place again in SAT~Competitions 2016 and 2017. 
Numerous applications, e.g., SMT solvers or SAT-based planners, use SAT solvers incrementaly, i.e., formulas are repeatedly refined between solve-calls. 
One important contribution of the founders of this track is the specification of the general incremental interface IPASIR (Re-entrant Incremental Solver API) for SAT applications~\cite{Balyo:2015:SATRace}. 
In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.

\paragraph{Backbone Variables}

The application $\mathsf{genipabones}$ creates the dual rail encoding~\cite{Balyo:2015:SATRace} of a given formula and incrementally checks for each variable if it is a backbone variable or not~\cite{Janota:2015:Backbones}. 
For this application, we selected $50$ of the smallest and easiest satisfiable problems from previous SAT competitions.

\paragraph{Essential Variables}

The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula~\cite{Bryant:1987:Essentials} by incrementally testing each variable using the dual-rail encoded formula. 
For this application, we used the same $50$ easy satisfiable problems as in the backbone variable detection application.

\paragraph{Longest Simple Paths}

@@

\paragraph{Maximum Satisfiability (MaxSAT)}

The application $\mathsf{genipamax}$ solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}. The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.

\paragraph{Quantified Boolean Formulas (QBF)}
The application $\mathsf{Ijtihad}$ is a QBF solver based on counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}. For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.

\paragraph{Planning}
The application $\mathsf{Pasar}$ is a planner which is based on the principles of counter-example guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}. 
For this application, we selected $50$ SAS planning instances.

@@

The SAT solvers of Armin Biere arguably belong to the best and most well-known independent code-bases. 
Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
CaDiCal came up in SAT Competition 2017 and has been award winning since then. 
Despite the fact that it seems very hard to lift the state-of-the-art with a completly new codebase, the new SAT solver Kissat by Armin Biere which was submitted for the first time this year set a new standard in sequential SAT solving in this competition (see Section~\ref{}).

ParaFrost by Osama and Wijs is another new codebase introducing several interesting new concepts~\cite{}. 
Its sequential variant was submitted for the first time in this competition.
